Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-03-19 paper/paper_before_maddie.tex
Updates from Overleaf

\begin{abstract}
%We introduce a method that uses generic programming tensor networks to compute various properties of a class of hard graph problems that can be decribed by local constraints.
We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
to compute various solution space properties of a class of combinatorial optimization problems specified by local constraints. \purple{I still think there is a more concise way to word the class of combinatorial optimization problems this works on...}\blue{changed a bit, better?}
%Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
We look at the independent set problem as an example, and show how to compute the size of the maximum independent set, count the number of independent sets of a given size, and enumerate the independent sets of a given size.
%By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
By using generic programming techniques, %which require a program to work correctly for different input data types without sacrificing efficiency,
the same general, simple-to-implement framework can be used to compute all of these properties. Our algorithm utilizes recent advances in tensor network contraction techniques to achieve high performance, including methods to quickly find a near-optimal contraction order and slicing.
The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the treewidth of the problem graph $G$.
Other hard graph problems solvable in our framework include the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others.
To demonstrate the versatility of this tool, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the overlap gap property on King's graphs at $0.8$ filling and 3-regular graphs, and visualizing the output of quantum optimization algorithms for the independent set problem. % including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
We show how our method helps to understand these hard problems better on systems with hundreds of vertices or spins. \xpurple{Say on systems with hundreds of vertices or spins?}
\end{abstract}

@@

\centerline{\begin{tikzpicture}[]
    \def\dx{0};
    \def\dy{0};
    \def\d{1};
    \def\a{1.0};
    \def\b{1};
    \def\ya{-1.0};
    \def\yb{-0.8};
    \node[] at (\dx+5*\a, \dy+5*\b) (R1) {$R[n^2]$};
    \node[] at (\dx+3*\a, \dy+4*\b) (S1) {$S_{bc}[n^3]$};
    \node[] at (\dx+2*\a, \dy+3*\b) (Q1) {$Q_{bd}[n^2]$};
    \node[] at (\dx+8.5*\a, \dy+3*\b) (Q2) {$Q_{bc}[n^2]$};
    \node[] at (\dx+\a, \dy+2*\b) (P1) {$P_{d}[n]$};
    \node[] at (\dx+9*\a, \dy+2*\b) (P2) {$P_{bc}[n^3]$};
    \node[] at (\dx+0.5*\d, \dy+\b) (M1) {$M_{d}[n^2]$};
    \node[] at (\dx+3.5*\d, \dy+\b) (M2) {$M_{bd}[n^2]$};
    \node[] at (\dx+5.5*\d, \dy+\b) (M3) {$M_{cd}[n^2]$};
    \node[] at (\dx+9.5*\d, \dy+\b) (M4) {$M_{ac}[n^2]$};
    \node[] at (\dx, \dy) (Bde) {$B_{de}$};
    \node[] at (\dx+\d, \dy) (We) {$W_e$};
    \node[] at (\dx+2*\d, \dy) (Wd) {$W_d$};
    \node[] at (\dx+3*\d, \dy) (Bbd) {$B_{bd}$};
    \node[] at (\dx+4*\d, \dy) (Wb) {$W_b$};
    \node[] at (\dx+5*\d, \dy) (Bcd) {$B_{cd}$};
    \node[] at (\dx+6*\d, \dy) (Wc) {$W_c$};
    \node[] at (\dx+7*\d, \dy) (Bbc) {$B_{bc}$};
    \node[] at (\dx+8*\d, \dy) (Bab) {$B_{ab}$};
    \node[] at (\dx+9*\d, \dy) (Bac) {$B_{ac}$};
    \node[] at (\dx+10*\d, \dy) (Wa) {$W_a$};
    \draw[] (Bde) -- (M1);
    \draw[] (We) -- (M1);
    \draw[] (Bbd) -- (M2);
    \draw[] (Wb) -- (M2);
    \draw[] (Bcd) -- (M3);
    \draw[] (Wc) -- (M3);
    \draw[] (Bac) -- (M4);
    \draw[] (Wa) -- (M4);
    \draw[] (M1) -- (P1);
    \draw[] (Wd) -- (P1);
    \draw[] (Bab) -- (P2);
    \draw[] (M4) -- (P2);
    \draw[] (P1) -- (Q1);
    \draw[] (M2) -- (Q1);
    \draw[] (Bbc) -- (Q2);
    \draw[] (P2) -- (Q2);
    \draw[] (Bbc) -- (Q2);
    \draw[] (P2) -- (Q2);
    \draw[] (Q1) -- (S1);
    \draw[] (M3) -- (S1);
    \draw[] (S1) -- (R1);
    \draw[] (Q2) -- (R1);
\end{tikzpicture}}
% \small{
% \begin{align*}
%     &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a, w_a)_{s_a} W(x_b, w_b)_{s_b} W(x_c, w_c)_{s_c} W(x_d, w_d)_{s_d} W(x_e, w_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_c s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}\\
%     =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e,w_e)_{s_e}\right) W(x_d,w_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b, w_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c, w_c)_{s_c}\right)\right)\right.\\
%     &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a,w_a)_{s_a}\right)\right)\right)\right)\\
%     =&1 + x_a^{w_a} + x_b^{w_b} + x_c^{w_c} + x_d^{w_d} + x_e^{w_e} + x_a^{w_a}x_d^{w_d} + x_a^{w_a}x_e^{w_e} + x_c^{w_c}x_e^{w_e} + x_b^{w_b}x_e^{w_e}
%     %=&1+5x+4x^2 \qquad \quad (x_{i} = x, w_{i}=1).
% \end{align*}}
The contraction process goes from bottom to top, where the root stores the contraction result that we want, the leaves are tensors in the our tensor network while the rest are all intermediate contraction results. Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor, and the contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of degrees of freedom, which in our case is always $2$.
One can easily check the largest tensor during computing has space complexity $n^2$, and the largest contraction time complexity is $n^3$, which is much smaller than direct enumeration ($n^5$).
\end{example}

@@

This algebra is a commutative semiring because we define the equivalence of two expression trees by comparing their expanded (using \Eq{eq:set}) forms, rather than their storages.
Although one is probably unable to enumerate the configurations represented by this tree due to the extremely large configuration space size,
but he can directly sample configurations from this tree.
This is because once we have this expression tree representation of the configuration space,
either generate by using this algebra directly or serve as the coefficients of (truncated) polynomials,
one can compute the number of configurations in each branch rigorously and efficiently.
%\purple{To clarify - is the expression tree now the coefficients
%on the polynomial? I am a little confused on how we would, for instance, use this to
%compute the MISs}\blue{added one more descriptive sentence, does it resolve your concern?}
To generate samples, one just descends this expression tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
\xpurple{How do we compute the size of each
branch?}
\begin{example}
Let us consider the following expression tree 
\begin{equation*}
    (\texttt{SUM}, /, (\texttt{PROD}, /, A, B), (\texttt{SUM}, /, C, D)),
\end{equation*}
where siblings $A, B, C$ and $D$ can be any four types of nodes.
It can be represented diagrammatically as the following.

@@

we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \text{ratio} \times \lfloor\alpha(G)\rfloor$ for each instance

@@

        \caption{$9$ Random three regular graphs of size $110$.}

@@

    \caption{The distribution of pairwise Hamming distances for configurations sampled from independent sets with sizes $\geq \lfloor{\rm ratio} \times \alpha(G)\rfloor$.

@@

\begin{figure} 
    \centering
    \includegraphics[width=.65\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/exp_configurations.pdf}
    \caption{A visualization of experimental outputs of a quantum algorithm for solving the maximum independent set problem.
    Each vertex represents an independent set, with edges between independent sets which differ by a swap operation or a vertex addition.}
    \label{fig:exp_configuratoins}
\end{figure}
The ability to enumerate configurations can also be used to understand the distribution of outputs from algorithms for solving the Maximum Independent Set problem.
This can give detailed insights to performance of the algorithm, such as if the algorithm is likely to return independent sets from certain clusters of local or global minima in the solution space.
As an example, we show in Figure~\ref{fig:exp_configuratoins} how our algorithm can be used to visualize experimental outputs of a quantum algorithm for solving the Maximum Independent Set problem using a programmable Rydberg atom array quantum computer~\cite{Ebadi2022}.
The structure of the solution space for a King's graph with $39$ vertices and filling factor $\rho=0.8$ can be visualized on a graph where each vertex represents a large independent set, with edges between independent sets which differ by a swap operation or a vertex addition.
The algorithm either finds the largest independent set with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
The algorithm does not appear to return local minima with large Hamming distance from the MISs as suggested by~\cite{altshuler2010}\blue{Fix ref.},
but samples from local minima with a wide range of Hamming distances from the MISs.
Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this particular King's graph.

\section{Discussion and conclusion}
In this paper, we introduce a method to use generic programming tensor networks to compute a number of different properties of a hard problem,
including the largest several independent sets sizes, the counting of independent sets of a given size and
the enumeration of independent sets of a given size.
For each solution space property, we design an algebra being a commutative semiring and let it be the tensor element type.
With different algebras, the contraction of the same tensor network gives us the different properties.
The data types introduced in the main text is summarized in the diagram in \Fig{fig:venn-diagram}.
Other than the case with real numbers, we have polynomials and truncated polynomials.
We combine them with the bit string algebra, the set algebra, and expression tree algebra for finding, enumeration, and sampling of independent sets at a given size.
These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}. 
Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
By adapting to the style of generic programming, we can implement all the algorithms without much effort.
We show some of the Julia language implementations in Appendix~\ref{sec:technical}.
A complete implementation can be found in our Github repository~\cite{GraphTensorNetworks}. 
We expect our tool can be used to understand and study many interesting applications of independent sets and beyond. We also hope this approach of generic tensor networks can inspire future works on tensor network computations.

\section*{Acknowledgments}
We would like to thank Pan Zhang for sharing his python code for optimizing contraction orders of a tensor network.
We acknowledge Sepehr Ebadi, and Leo Zhou for coming up with many interesting questions about independent sets and their questions strongly motivated the development of this project.
We thank Benjamin Schiffer for providing helpful advices about writing.
We thank Chris Elord for helping us to write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!
We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, and Katharine Hyatt,
for actively maintaining their packages and resolving related issues voluntarily.
\blue{funding information}

>>>>

\begin{abstract}
%We introduce a method that uses generic programming tensor networks to compute various properties of a class of hard graph problems that can be decribed by local constraints.
We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
to compute various solution space properties of a class of combinatorial optimization problems specified by local constraints. \purple{I still think there is a more concise way to word the class of combinatorial optimization problems this works on...}\blue{changed a bit, better?}
%Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
We look at the independent set problem as an example, and show how to compute the size of the maximum independent set, count the number of independent sets of a given size, and enumerate the independent sets of a given size.
%By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
By using generic programming techniques, %which require a program to work correctly for different input data types without sacrificing efficiency,
the same simple-to-implement framework can be used to compute all of these properties. Our algorithm utilizes recent advances in tensor network contraction techniques to achieve high performance, including methods to quickly find a near-optimal contraction order and slicing.
The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the treewidth of the problem graph $G$.
Other hard graph problems solvable in our framework include the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others.
To demonstrate the versatility of this tool, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the overlap gap property on King's graphs at $0.8$ filling and 3-regular graphs, and visualizing the output of quantum optimization algorithms for the independent set problem. \purple{I might not directly mention the classes of graphs we look at for overlap gap - it might be too much information. I'm not sure though, what do you think?} % including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
We show how our method helps to understand these hard problems on systems with hundreds of vertices.
\end{abstract}

@@

\centerline{\begin{tikzpicture}[]
    \def\dx{0};
    \def\dy{0};
    \def\d{1};
    \def\a{1.0};
    \def\b{1};
    \def\ya{-1.0};
    \def\yb{-0.8};
    \node[] at (\dx+5*\a, \dy+5*\b) (R1) {$R[n^2]$};
    \node[] at (\dx+3*\a, \dy+4*\b) (S1) {$S_{bc}[n^3]$};
    \node[] at (\dx+2*\a, \dy+3*\b) (Q1) {$Q_{bd}[n^2]$};
    \node[] at (\dx+8.5*\a, \dy+3*\b) (Q2) {$Q_{bc}[n^2]$};
    \node[] at (\dx+\a, \dy+2*\b) (P1) {$P_{d}[n]$};
    \node[] at (\dx+9*\a, \dy+2*\b) (P2) {$P_{bc}[n^3]$};
    \node[] at (\dx+0.5*\d, \dy+\b) (M1) {$M_{d}[n^2]$};
    \node[] at (\dx+3.5*\d, \dy+\b) (M2) {$M_{bd}[n^2]$};
    \node[] at (\dx+5.5*\d, \dy+\b) (M3) {$M_{cd}[n^2]$};
    \node[] at (\dx+9.5*\d, \dy+\b) (M4) {$M_{ac}[n^2]$};
    \node[] at (\dx, \dy) (Bde) {$B_{de}$};
    \node[] at (\dx+\d, \dy) (We) {$W_e$};
    \node[] at (\dx+2*\d, \dy) (Wd) {$W_d$};
    \node[] at (\dx+3*\d, \dy) (Bbd) {$B_{bd}$};
    \node[] at (\dx+4*\d, \dy) (Wb) {$W_b$};
    \node[] at (\dx+5*\d, \dy) (Bcd) {$B_{cd}$};
    \node[] at (\dx+6*\d, \dy) (Wc) {$W_c$};
    \node[] at (\dx+7*\d, \dy) (Bbc) {$B_{bc}$};
    \node[] at (\dx+8*\d, \dy) (Bab) {$B_{ab}$};
    \node[] at (\dx+9*\d, \dy) (Bac) {$B_{ac}$};
    \node[] at (\dx+10*\d, \dy) (Wa) {$W_a$};
    \draw[] (Bde) -- (M1);
    \draw[] (We) -- (M1);
    \draw[] (Bbd) -- (M2);
    \draw[] (Wb) -- (M2);
    \draw[] (Bcd) -- (M3);
    \draw[] (Wc) -- (M3);
    \draw[] (Bac) -- (M4);
    \draw[] (Wa) -- (M4);
    \draw[] (M1) -- (P1);
    \draw[] (Wd) -- (P1);
    \draw[] (Bab) -- (P2);
    \draw[] (M4) -- (P2);
    \draw[] (P1) -- (Q1);
    \draw[] (M2) -- (Q1);
    \draw[] (Bbc) -- (Q2);
    \draw[] (P2) -- (Q2);
    \draw[] (Bbc) -- (Q2);
    \draw[] (P2) -- (Q2);
    \draw[] (Q1) -- (S1);
    \draw[] (M3) -- (S1);
    \draw[] (S1) -- (R1);
    \draw[] (Q2) -- (R1);
\end{tikzpicture}}
% \small{
% \begin{align*}
%     &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a, w_a)_{s_a} W(x_b, w_b)_{s_b} W(x_c, w_c)_{s_c} W(x_d, w_d)_{s_d} W(x_e, w_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_c s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}\\
%     =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e,w_e)_{s_e}\right) W(x_d,w_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b, w_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c, w_c)_{s_c}\right)\right)\right.\\
%     &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a,w_a)_{s_a}\right)\right)\right)\right)\\
%     =&1 + x_a^{w_a} + x_b^{w_b} + x_c^{w_c} + x_d^{w_d} + x_e^{w_e} + x_a^{w_a}x_d^{w_d} + x_a^{w_a}x_e^{w_e} + x_c^{w_c}x_e^{w_e} + x_b^{w_b}x_e^{w_e}
%     %=&1+5x+4x^2 \qquad \quad (x_{i} = x, w_{i}=1).
% \end{align*}}
The contraction process goes from bottom to top, where the root stores the contraction result that we want, the leaves are tensors in the our tensor network while the rest nodes are all intermediate contraction results.
Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor and the largest number of subscripts is the treewidth of the original $5$-vertex graph. The contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of degrees of freedom, which in our case is always $2$.
One can easily check the largest tensor during computing has space complexity $n^2$, i.e. the treewidth of the original $5$-vertex graph is $2$, and the largest contraction time complexity is $n^3$, which is much smaller than the direct enumeration ($n^5$).
\end{example}

@@

This algebra is a commutative semiring because we define the equivalence of two expression trees by comparing their expanded (using \Eq{eq:set}) forms, rather than their storages.
Although one is probably unable to enumerate the configurations represented by this tree due to the extremely large configuration space size,
but he can directly sample configurations from this tree.
This is because once we have this expression tree representation of the configuration space,
either generate by using this algebra directly or serve as the coefficients of (truncated) polynomials,
one can compute the number of configurations in each branch rigorously and efficiently.
To generate samples, one just descends this expression tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
\begin{example}
Let us consider the following expression tree 
\begin{equation*}
    (\texttt{SUM}, /, (\texttt{PROD}, /, A, B), (\texttt{SUM}, /, C, D)),
\end{equation*}
where siblings $A, B, C$ and $D$ can be any four types of nodes.
It can be represented diagrammatically as the following.

@@

we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \lfloor (1-\text{ratio}) \times \alpha(G)\rfloor$ for each instance

@@

        \caption{$9$ random three regular graphs of size $110$.}

@@

    \caption{The distribution of pairwise Hamming distances for configurations sampled from independent sets with sizes $\geq \lfloor(1-{\rm ratio}) \times \alpha(G)\rfloor$.

@@

\begin{figure} 
    \centering
    \includegraphics[width=.65\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/exp_configurations.pdf}
    \caption{A visualization of experimental outputs of a quantum algorithm for solving the maximum independent set problem.
    Each vertex represents an independent set, and each edge represents a pair of  independent sets that differ by a swap operation or a vertex addition.}
    \label{fig:exp_configuratoins}
\end{figure}
The ability to enumerate configurations can also be used to understand the distribution of outputs from algorithms for solving the Maximum Independent Set problem.
This can give detailed insights to performance of the algorithm, such as if the algorithm is likely to return independent sets from certain clusters of local or global minima in the solution space.
As an example, we show in Figure~\ref{fig:exp_configuratoins} how our algorithm can be used to visualize experimental outputs of a quantum algorithm for solving the Maximum Independent Set problem using a programmable Rydberg atom array quantum computer~\cite{Ebadi2022}.
The structure of the solution space for a King's graph with $39$ vertices and filling factor $\rho=0.8$ can be visualized on a graph where each vertex represents a large independent set, with edges between independent sets which differ by a swap operation or a vertex addition.
The algorithm either finds the largest independent set with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
The algorithm does not appear to return local minima with large Hamming distance from the MISs as suggested by~\cite{altshuler2010}\blue{Fix ref.},
but samples from local minima with a wide range of Hamming distances from the MISs.
Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this particular King's graph.

\section{Discussion and conclusion}
In this paper, we introduce a method to use generic programming and tensor networks to compute a number of different solution space properties of the maximum independent set problem,
including the largest several independent sets sizes, the number of independent sets of a given size, and
the enumeration of independent sets of a given size.
For each solution space property, we design a commutative semiring algebra for the tensor element type.
With different algebras, the contraction of the same tensor network gives us the different properties.
The data types introduced in the main text is summarized in the diagram in \Fig{fig:venn-diagram}.
Other than the case with real numbers, we have polynomials and truncated polynomials.
We combine them with the bit string algebra, the set algebra, and expression tree algebra for finding, enumeration, and sampling of independent sets at a given size.
These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}. 
Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
By adapting to the style of generic programming, we can implement all the algorithms without much effort.
We show some of the Julia language implementations in Appendix~\ref{sec:technical}.
A complete implementation can be found in our Github repository~\cite{GraphTensorNetworks}. 
We expect our tool can be used to understand and study many interesting applications of independent sets and beyond. We also hope this approach of generic tensor networks can inspire future works on tensor network computations.

\section*{Acknowledgments}
We would like to thank Pan Zhang for sharing his python code for optimizing contraction orders of a tensor network.
We acknowledge Sepehr Ebadi and Leo Zhou for coming up with many interesting questions about independent sets and their questions strongly motivated the development of this project.
We thank Benjamin Schiffer for providing helpful feedback on the manuscript.
We thank Chris Elord for helping us write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!
We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, and Katharine Hyatt
for actively maintaining their packages and resolving related issues voluntarily.
\blue{funding information}
